---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  warning=FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

Package ggiraphExtra contains many useful functions for exploratory plots. These functions are made by both 'ggplot2' and 'ggiraph' packages. You can make a static ggplot or an interactive ggplot by setting the parameter interactive=TRUE.

## Package installation

You can install package ggiraphExtra from CRAN with the following command.

```{r,warning=FALSE,message=FALSE,eval=FALSE}
install.packages("ggiraphExtra")
```

You can install the latest version of ggiraphExtra from github.

```{r,warning=FALSE,message=FALSE,eval=FALSE}
#install.packages("devtools")
devtools::install_github("cardiomoon/ggiraphExtra")
```

## Full version of this vignette

You can find the full version of this vignette at http://rpubs.com/cardiomoon/231820


## Shiny app for interactive plot 

You can find the shiny app for interactive plot using the ggiraphExtra package at:

http://web-r.org:3838/explore

http://r-ggplot2.com:3838/explore

http://web-r.club:3838/explore

