---
title: "package ggiraphExtra"
author: "Keon-Woong Moon"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{package ggiraphExtra}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Package ggiraphExtra contains many useful functions for exploratoty plots. These functions are made by both 'ggplot2' and 'ggiraph' packages. You can make a static ggplot or an interactive ggplot by setting the parameter interactive=TRUE.

## Package installation

You can install package ggiraphExtra with the following command.

```{r,warning=FALSE,message=FALSE,eval=FALSE}
#install.packages("devtools")
devtools::install_github("cardiomoon/ggiraphExtra")
```

## ggPoints() for interactive scatterplot with regression equation

You can make interactive ggplot easily. You can hover the points, see the regression equations and zoom-in zoom-out with the mouse wheel.  

```{r,warning=FALSE,message=FALSE}
require(ggplot2)
require(ggiraph)
require(ggiraphExtra)

ggPoints(aes(x=wt,y=mpg,color=am),data=mtcars,method="lm",interactive=TRUE)
```

You can draw scatter plot for binary dependent variable. The `GBSG2` data contains data of 686 observations from the German Breast Cancer Study Group 2(GBSG2) study. You can get logistic regression line with a jittered scatterplot by setting the parameter `method` `glm`.

```{r,message=FALSE,warning=FALSE}
require(TH.data)
data(GBSG2)
ggPoints(aes(x=pnodes,y=cens),data=GBSG2,method="glm",interactive=TRUE)
```

Please check the vignette for "ggPoints" at http://rpubs.com/cardiomoon/231822

## ggRadar() for interactive radar chart

You can explore a data.frame with ggRadar() or ggBoxplot().

```{r,warning=FALSE,message=FALSE}
ggRadar(data=iris,aes(color=Species),interactive=TRUE)
ggRadar(data=mtcars,aes(colour=am),interactive=TRUE)
```

## ggSpine() for an interactive spinogram

ggSpine() is a interactive ggplot version of spineplot(). Spine plots are a special cases of mosaic plots, and can be seen as a generalization of stacked (or highlighted) bar plots. Analogously, spinograms are an extension of histograms. You can add labels by setting the parameter addlabel=TRUE.
```{r,warning=FALSE,message=FALSE}
require(moonBook)
ggSpine(data=acs,aes(x=age,fill=smoking),interactive=TRUE)
ggSpine(data=acs,aes(x=Dx,fill=smoking),addlabel=TRUE,interactive=TRUE)
```
## ggBar() for an interactive barplot 

ggBar() draws interactive barplot. You can add labels, draw horizontal barplots or polar plots. You can draw histogram with ggBar()

```{r,warning=FALSE,message=FALSE}
ggBar(acs,aes(x=Dx,fill=smoking),addlabel=TRUE,horizontal=TRUE,width=0.5,interactive=TRUE)
ggBar(rose,aes(x=Month,fill=group,y=value),stat="identity",polar=TRUE,palette="Reds",width=1,
       color="black",size=0.1,interactive=TRUE)
ggBar(acs,aes(x=age,fill=smoking),addlabel=TRUE,horizontal=TRUE,width=0.5,interactive=TRUE)
```


## ggPair() for an interactive scatter plot with line plot

```{r,warning=FALSE,message=FALSE}
ggPair(iris[3:5],interactive=TRUE)
ggPair(iris,aes(color=Species),horizontal=TRUE,interactive=TRUE)
```

## ggPieDonut() for a pie and donut plot

You can draw a pie and donut plot with ggPieDonut().

```{r,warning=FALSE,message=FALSE}
ggPieDonut(acs,aes(pies=Dx,donuts=smoking),interactive=TRUE)
ggPieDonut(browsers,aes(pies=browser,donuts=version,count=share),interactive=TRUE)
ggDonut(browsers,aes(donuts=version,count=share),interactive=TRUE)
```

## ggCLE() for a cleveland dot plot

```{r,warning=FALSE,message=FALSE}
require(gcookbook)
mtcars$name=rownames(mtcars)
ggCLE(data=mtcars,aes(x=mpg,y=name,color=am,facet=am),interactive=TRUE)
ggCLE(data=tophitters2001,aes(x=avg,y=name,color=lg,facet=lg),no=20,interactive=TRUE)
```

## Full version of this vignette

You can find the full version of this vignette at http://rpubs.com/cardiomoon/231820
